\Large \bf Frontrunning

### 2018-08-15 frontrunning/Latex/sections/paper.tex
[frontrunning] Some text here and there.

\subsubsection{Miners}
As mentioned above, since the Blockchain miners are the only parties who can decide on the order of transactions within a block they mine, they can easily intercept and reorder the pending transactions sitting in the mempool and profit from a guaranteed price-rise. For example in an Ethereum based application, a miner learns about the pending \textit{buy} transaction of 1000 Ether, presumably if this transaction goes through, it causes the price of Ether to increase. So the dishonest miner can step in front of this transaction and  place his own buy order ahead of it. He would simply create his \textit{buy} of 1000 Ether and include it within a block and now he mines the previous \textit{buy} transaction of 1000 Ether. Doing so, he would receive a better rate than other network users, can sell the assets he has received and gain a price advantage at the expense of others. Similarly, a dishonest miner can sell his tokens in front, if he sees a pending \textit{sell} transaction. In an open source blockchain application, there is no rules on how transactions must be ordered and miners are free to send transactions in the order they prefer. However, miners can only front run other transactions (by reordering them) within the block they happen to mine while they do not broadcast any transactions to the network. This makes the miners to be less noticeable to the network when front running.

\subsubsection{Blockchain users/nodes}
Any regular (non-miner or miner) user can also front-run other transactions in the network. For regular users to front run others on the blockchain, they need to be fully/well connected to other nodes on the network. Doing so, they are able to listen to the network and monitor all transactions that are broadcast. On the Ethereum blockchain users have to pay for the computations in small amount of Ether called \textit{gas}~\cite{AccountT67:online}. The price that users pay for transactions (a.k.a. transaction fees) can increase or decrease how quickly they are executed and included within the blocks by the miners.  This is because the Ethereum miners consume resources to process the transactions and so receive the transaction fees after creating the blocks. Once seeing two identical transactions with different transaction fees, profit maximizers miners are free to mine select the transaction which offers the highest fee. Therefore, any regular users who run a full-node Ethereum client can modify the order of pending transactions by paying a more amount of gas \ie by monitoring the network, upon seeing a  pending \textit{buy} transaction which will further increase the price of the asset, a font-runner user can pay a higher gas price and send his transaction a head of that. By doing so, he achieves a better rate from any other network users. Note that in this case, blockchain front runners are more visible to the network as they broadcast their transactions to all the network participants.

@@

\section{How to stop frontrunning?}

>>>>

\subsubsection{Miners}
As mentioned above, since the Blockchain miners are the only parties who can decide on the order of transactions within a block they mine, they can easily intercept and reorder the pending transactions sitting in the mempool and profit from a guaranteed price-rise. For example in an Ethereum based application, a miner learns about the pending \textit{buy} transaction of 1000 units of a token, i.e. TKN, presumably if this transaction goes through, it causes the price the purchased token to increase. So the dishonest miner can step in front of this transaction and  place his own buy order ahead of it. He would simply create his \textit{buy} of 1000 TKN and include it within a block and now he mines the previous \textit{buy} transaction of 1000 TKN. Doing so, he would receive a better rate than other network users, and can sell the assets he has received and gain a price advantage at the expense of others. Similarly, a dishonest miner can sell his tokens in front, if he sees a pending \textit{sell} transaction. In an open source blockchain application, there is no rules on how transactions must be ordered and miners are free to send transactions in the order they prefer. However, miners can only front run other transactions (by reordering them) within the block they happen to mine. They could do this also by not broadcasting their own transactions to the network, this makes the miners to be less noticeable to the network when front running.
Another example here is in the case of decentral exchanges and order cancellation. Every exchange should have the functionality to cancel the orders, especially for a volatile market. In this case, when user decides that her order is not profitable anymore, she would send a cancelation transaction. Here the miner sees the cancelation transaction and puts his own order before the cancellation transaction to fill the order, potentially profiting from the order. They can also include the canceled transaction in their block to collect the full gas limit used by that transaction~\cite{CostofDecentralization:online}.

\subsubsection{Blockchain users/nodes}
Any regular (non-miner or miner) user can also front-run other transactions in the network. For regular users to front run others on the blockchain, they need to be fully/well connected to other nodes on the network. Doing so, they are able to listen to the network and monitor all transactions that are broadcast. On the Ethereum blockchain users have to pay for the computations in small amount of Ether called \textit{gas}~\cite{AccountT67:online}. The price that users pay for transactions (a.k.a. transaction fees) can increase or decrease how quickly miners will execute them and include them within the block they mine. This is because the Ethereum miners consume resources to process the transactions and so receive the transaction fees after creating the blocks. Once seeing two identical transactions with different transaction fees, 
%Given the limited space in the blocks, a rational miner will prioritize transactions that pay higher gas price per unit of gas, this maximizes their profit in the block they mine.
miners act to maximize their profit and are free to mine the transaction which offers the highest fee. Therefore, any regular users who run a full-node Ethereum client can modify the order of pending transactions by paying with a higher gas price\ie by monitoring the network, upon seeing a  pending \textit{buy} transaction which will further increase the price of the asset, a font-runner user can pay a higher gas price and hope to have his transaction a head of the other one mined. By doing so, he achieves a better rate from the other network users. Note that in this case, blockchain front runners are more visible to the network as they broadcast their transactions to all the network participants.

@@

\section{How to stop frontrunning?}
In the traditional markets, frontrunning is considered unethical and also illegal. In the blockchain space, the designers of the decentral applications cannot rely on the justice system for unethical behaviour, and they must assume that each participant in the network acts rationally in their own self interest, the application will be operating in an adversarial environment~\cite{0xfrontrunning:online}.
